Figure code

### 2022-06-10 figures/figures.Rmd
correct figure plot code

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(ggtextures)
```

@@

```{r}
### try and draw the apple one again with color
tools_w_categories_and_image <- meta_data %>% 
  mutate(image_single = case_when(
    categories_alphabetically == "Block/removal" ~ "1_block",
    categories_alphabetically == "Goal-advancement" ~ "1_goal",
    categories_alphabetically == "Self-tracking" ~ "1_track",
    categories_alphabetically == "Reward/punish" ~ "1_reward",
    categories_alphabetically == "Block/removal + Goal-advancement" ~ "2_block_goal",
    categories_alphabetically == "Block/removal + Reward/punish" ~ "2_block_reward",
    categories_alphabetically == "Block/removal + Self-tracking" ~ "2_block_track",
    categories_alphabetically == "Goal-advancement + Reward/punish" ~ "2_goal_reward",
    categories_alphabetically == "Goal-advancement + Self-tracking" ~ "2_track_goal",
    categories_alphabetically == "Reward/punish + Self-tracking" ~ "2_track_reward",
    categories_alphabetically == "Block/removal + Goal-advancement + Self-tracking" ~ "3_block_track_goal",
    categories_alphabetically == "Block/removal + Reward/punish + Self-tracking" ~ "3_block_track_reward",
    categories_alphabetically == "Goal-advancement + Reward/punish + Self-tracking" ~ "3_goal_track_reward",
    categories_alphabetically == "Block/removal + Goal-advancement + Reward/punish + Self-tracking" ~ "4_all",
  )) %>% 
  mutate(image_single = str_c(here::here("figures", "plot_colours/"), image_single, ".png")) %>% 
  select(tool_id, title, num_ratings, min_installs, num_users, store, image_single)

@@

# Plot of tools by user numbers
generate apple plot
```{r}
apple_data <- tools_w_categories_and_image %>% 
  filter(store == "apple") %>% 
  filter(num_ratings > 0)

@@

save_plot(here::here("figures", "apple_ratings_and_features.png"), test_apple,
          # each individual subplot should have an aspect ratio of 1.3
          base_aspect_ratio = 1.8
          )
```

generate google play plot

@@

(play_combined <- plot_grid(play_install_bar, play_feature_plot, rel_widths = c(4,1), labels = c("Google Play", "Features"), hjust = "left", label_x = c(0.02, 0.075), label_y = 1))

@@

generate chrome web plot

@@

put them all together

@@

# create the boxplot
# with store
boxplot_ratings <- meta_data %>%
  filter(num_ratings > ratings_more_than) %>%
  mutate(categories_alphabetically = factor(categories_alphabetically, levels = rev(ave_ratings_levels), ordered = TRUE)) %>%
  ggplot(aes(x = categories_alphabetically, y = average_rating)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.3, height = 0.1, size = 1.1, alpha = 0.7) +
    theme_minimal() +
    labs(x = "", y = "") +
    coord_flip() +
    theme(axis.text.y=element_blank()) +
    theme(plot.margin = margin(1.5, 0, 0, 0, "cm")) +
    scale_y_continuous(limits = c(1,5))

@@

ggsave(here::here("figures", "ratings_by_type_annotated.pdf"), height = 4.3, width = 7)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(ggtextures) #remotes::install_github("clauswilke/ggtextures") 
```

@@

```{r}
# set up the mapping between categories and colors
tools_w_categories_and_image <- meta_data %>% 
  mutate(image_single = case_when(
    categories_alphabetically == "Block/removal" ~ "1_block",
    categories_alphabetically == "Goal-advancement" ~ "1_goal",
    categories_alphabetically == "Self-tracking" ~ "1_track",
    categories_alphabetically == "Reward/punish" ~ "1_reward",
    categories_alphabetically == "Block/removal + Goal-advancement" ~ "2_block_goal",
    categories_alphabetically == "Block/removal + Reward/punish" ~ "2_block_reward",
    categories_alphabetically == "Block/removal + Self-tracking" ~ "2_block_track",
    categories_alphabetically == "Goal-advancement + Reward/punish" ~ "2_goal_reward",
    categories_alphabetically == "Goal-advancement + Self-tracking" ~ "2_track_goal",
    categories_alphabetically == "Reward/punish + Self-tracking" ~ "2_track_reward",
    categories_alphabetically == "Block/removal + Goal-advancement + Self-tracking" ~ "3_block_track_goal",
    categories_alphabetically == "Block/removal + Reward/punish + Self-tracking" ~ "3_block_track_reward",
    categories_alphabetically == "Goal-advancement + Reward/punish + Self-tracking" ~ "3_goal_track_reward",
    categories_alphabetically == "Block/removal + Goal-advancement + Reward/punish + Self-tracking" ~ "4_all",
  )) %>% 
  mutate(image_single = str_c(here::here("figures", "plot_colours/"), image_single, ".png")) %>% 
  select(tool_id, title, num_ratings, min_installs, num_users, store, image_single)

@@

# Plot of tools by user numbers
## generate apple plot
```{r}
apple_data <- tools_w_categories_and_image %>% 
  filter(store == "apple") %>% 
  filter(num_ratings > 0)

@@

save_plot(here::here("figures", "apple_ratings_and_features.png"), apple_combined,
          # each individual subplot should have an aspect ratio of 1.3
          base_aspect_ratio = 1.8
          )
```

## generate google play plot

@@

play_combined <- plot_grid(play_install_bar, play_feature_plot, rel_widths = c(4,1), labels = c("Google Play", "Features"), hjust = "left", label_x = c(0.02, 0.075), label_y = 1)

@@

## generate chrome web store plot

@@

## Combine them

@@

# create the boxplot
# with store
boxplot_ratings <- meta_data %>%
  filter(num_ratings > ratings_more_than) %>%
  mutate(categories_alphabetically = factor(categories_alphabetically, levels = rev(ave_ratings_levels), ordered = TRUE)) %>%
  rename(Store = store) %>% 
  ggplot(aes(x = categories_alphabetically, y = average_rating)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.34, height = 0.06, size = 1.1, alpha = 0.8, aes(fill = Store, shape = Store)) +
    theme_minimal() +
    labs(x = "", y = "") +
    coord_flip() +
    theme(axis.text.y=element_blank(), plot.margin = margin(1.5, 0, 0, 0, "cm"), legend.position="left", legend.box.margin=margin(0,-0.5,0,0, "cm")) +
    scale_y_continuous(limits = c(1,5)) +
    scale_fill_manual(values = c("darkgrey", "#f0027f", "white")) +
    scale_shape_manual(values = c(22, 21, 25))

@@

ggsave(here::here("figures", "ratings_by_type_annotated.pdf"), height = 4.3, width = 7)
